Modelling the emergence of whisker barrels

### 2020-06-18 paper/briefpaper/brief.tex
Adds text and reference for minor point 4

% Blue changes are mostly major points 2 (competition mechanism) and 3 (parameter/sensitivity)
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
% Red for Stuart's updates
\newcommand{\stu}[1]{\textcolor{red}{#1}}
% Minor point 6:
\newcommand{\mpsix}[1]{\textcolor{revpurp}{#1}}

@@

Barrel formation requires afferent input from whisker stimulation and thalamic
calcium waves \citep{anton-bolanos_prenatal_2019}, and depends on a complex
network of axon guidance molecules such as ephrin-A5 and A7 and adhesion
molecules such as cadherin-6 and 8
\citep{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}.  This network
is orchestrated by interactions between morphogens Fgf8 and Fgf17 and
transcription factors Emx2, Pax6, Sp8, and Coup-tf1
\citep{shimogori_fibroblast_2005,bishop_regulation_2000}, which are expressed
in gradients that mark orthogonal axes and can be manipulated to stretch,
shrink, shift, and even duplicate barrels
\citep{assimacopoulos_fibroblast_2012}.

@@

A cortical boundary enclosing 41 \cmnt{macrovibrissae} barrels was traced from
a cytochrome oxidase stain from \cite{zheng_signal_2001} \cmnt{(using the
  authors' original data)}, and Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved
for $N=41$ projections on the resulting domain, using $M=2$ linear signalling
gradients aligned with the anterior-posterior and medial-lateral axes. From
random initial conditions for $a(\mb{x},0)$, \cmnt{with each hexagonal element
  of $a_i$ set from a uniform distribution according to $0.2+{U}(0,0.2)$, and
  $c(\mb{x},0)=0$}, a clear Voronoi-like tesselation
emerged (Fig.\,\ref{fig:main}C; see Movie S1). A reduction in the Honda delta
metric (see \citealp{senft_mouse_1991}) confirmed that a `good' Voronoi
pattern emerged within \cmnt{$\approx$~20000} iterations
(Fig.\,\ref{fig:main}D).  A measure of the difference in \cmnt{barrel area}
between real and simulated barrels revealed a strong correspondence (see
Fig.\,\ref{fig:main}D, squares). \cmnt{In a chosen region, the ratio of
  \emph{the connection density of the TC type $i$ which makes the densest
    connections} to \emph{the sum of all connection densities} gives a measure
  of the selectivity of the connection density, $\mu(\mb{x},t)$. We summed this measure
  across the entire barrel domain and named it $\omega(t)$ (see
  Fig.\,\ref{fig:main}D, grey hexagons). $\omega$ increases during the first
  20000 simulation steps and converges on a stable
  value. Fig.\,\ref{fig:main}E shows the selectivity measure plotted as a
  luminance map, giving a more graded impression of the structure which
  develops in the system.}

>>>>

% Blue changes are mostly major points 2 (competition mechanism) and 3 (parameter/sensitivity)
\newcommand{\cmnt}[1]{\textcolor{blue}{#1}}
% Red for Stuart's updates
\newcommand{\stu}[1]{\textcolor{red}{#1}}
% Minor point 4:
\newcommand{\mpfour}[1]{\textcolor{revgreen}{#1}}
% Minor point 6:
\newcommand{\mpsix}[1]{\textcolor{revpurp}{#1}}

@@

Barrel formation requires afferent input from whisker stimulation and thalamic
calcium waves \citep{anton-bolanos_prenatal_2019}, and depends on a complex
network of axon guidance molecules such as ephrin-A5 and A7 and adhesion
molecules such as cadherin-6 and 8
\citep{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}.  This network
is orchestrated by interactions between morphogens Fgf8 and Fgf17 and
transcription factors Emx2, Pax6, Sp8, and Coup-tf1
\citep{shimogori_fibroblast_2005,bishop_regulation_2000}, which are expressed
in gradients \mpfour{across the full cortical sheet} that mark orthogonal axes
and can be manipulated to stretch,
shrink, shift, and even duplicate barrels
\citep{assimacopoulos_fibroblast_2012}.

@@

A cortical boundary enclosing 41 \cmnt{macrovibrissae} barrels was traced from
a cytochrome oxidase stain from \cite{zheng_signal_2001} \cmnt{(using the
  authors' original data)}, and Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved
for $N=41$ projections on the resulting domain, using $M=2$ linear signalling
gradients aligned with the anterior-posterior and medial-lateral axes.
%
\mpfour{The signalling gradients are assumed not to interact with the barrel
  field boundary and to continue well beyond its extent (see
  \citealp{miller_epha7-ephrin-a5_2006}, their Fig.\,11) in order to
  participate in other developmental processes, such as inter-area positional
  specification \citep{sur_patterning_2005,oleary_area_2007}.} % Just oleary_area_2007 would be ok
%
From
random initial conditions for $a(\mb{x},0)$, \cmnt{with each hexagonal element
  of $a_i$ set from a uniform distribution according to $0.2+{U}(0,0.2)$, and
  $c(\mb{x},0)=0$}, a clear Voronoi-like tesselation
emerged (Fig.\,\ref{fig:main}C; see Movie S1). A reduction in the Honda delta
metric (see \citealp{senft_mouse_1991}) confirmed that a `good' Voronoi
pattern emerged within \cmnt{$\approx$~20000} iterations
(Fig.\,\ref{fig:main}D).  A measure of the difference in \cmnt{barrel area}
between real and simulated barrels revealed a strong correspondence (see
Fig.\,\ref{fig:main}D, squares). \cmnt{In a chosen region, the ratio of
  \emph{the connection density of the TC type $i$ which makes the densest
    connections} to \emph{the sum of all connection densities} gives a measure
  of the selectivity of the connection density, $\mu(\mb{x},t)$. We summed this measure
  across the entire barrel domain and named it $\omega(t)$ (see
  Fig.\,\ref{fig:main}D, grey hexagons). $\omega$ increases during the first
  20000 simulation steps and converges on a stable
  value. Fig.\,\ref{fig:main}E shows the selectivity measure plotted as a
  luminance map, giving a more graded impression of the structure which
  develops in the system.}
